More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\mprset{myfraction=\reddottedrule}\inferrule
		{
			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}

>>>>

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\mprset{myfraction=\reddottedrule}\inferrule
		{
			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{important comment added:}
Note that this does not mean that any two pNets can be composed and produce an open 
transition. Indeed, the predicate $\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q}$ might not 
be satisfiable if the open transition of $Q$ cannot be matched with $\beta_{j_0}$.

\LUDO{Question/comment: this formulation makes the proof easy and supposes that we use 
enough 
variables, which is in accordance with the implementation and the way we define SV, but I 
believe that $\Pred\,'\land \beta_{j_0}= v_Q$ might be better because more flexible and 
less dependant of the way OTs are defined}

\begin{small}
